Marketing Analysis

### 2016-04-18 articles/articles.Rmd
upload
organize folder

- Principles of good data analytics. [[blog](http://www.gregreda.com/2014/03/23/principles-of-good-data-analysis/)] 
- Why I Ditched My Fitbit and What This Means for Analytics. [[Data Science Central](http://www.datasciencecentral.com/profiles/blogs/why-i-ditched-my-fitbit-and-what-this-means-for-analytics)]
- Know the Difference between Customer Service and Customer Experience. [[Harvard Business Review](https://hbr.org/sponsored/2016/03/know-the-difference-between-customer-service-and-customer-experience?utm_source=twitter&utm_medium=social&utm_campaign=harvardbiz)]
- Two articles about saying no to p-values. [[R-bloggers](http://www.r-bloggers.com/after-150-years-the-asa-says-no-to-p-values/)][[R-bloggers](http://www.r-bloggers.com/its-not-the-p-values-fault-reflections-on-the-recent-asa-statement-relevant-r-resources/)]
- The 9 Best Marketing And Sales Analytics You Should Know About.[[Data Science Central](http://www.datasciencecentral.com/profiles/blogs/the-9-best-marketing-and-sales-analytics-you-should-know-about)]
- Cohort analysis. [[Youtube](https://www.youtube.com/watch?v=NyhVdGmnh0I)]
- Ted Talk : How to use data to make a hit TV show. [[Ted](http://www.ted.com/talks/sebastian_wernicke_how_to_use_data_to_make_a_hit_tv_show?utm_campaign=social&utm_medium=referral&utm_source=facebook.com&utm_content=talk&utm_term=technology)]

@@

>>>>

- Doing Data Science Right — Your Most Common Questions Answered. [[Review](http://firstround.com/review/doing-data-science-right-your-most-common-questions-answered/?imm_mid=0e29cf&cmp=em-data-na-na-newsltr_20160413)]
- Principles of good data analytics. [[blog](http://www.gregreda.com/2014/03/23/principles-of-good-data-analysis/)] 
- Why I Ditched My Fitbit and What This Means for Analytics. [[Data Science Central](http://www.datasciencecentral.com/profiles/blogs/why-i-ditched-my-fitbit-and-what-this-means-for-analytics)]
- Know the Difference between Customer Service and Customer Experience. [[Harvard Business Review](https://hbr.org/sponsored/2016/03/know-the-difference-between-customer-service-and-customer-experience?utm_source=twitter&utm_medium=social&utm_campaign=harvardbiz)]
- Two articles about saying no to p-values. [[R-bloggers](http://www.r-bloggers.com/after-150-years-the-asa-says-no-to-p-values/)][[R-bloggers](http://www.r-bloggers.com/its-not-the-p-values-fault-reflections-on-the-recent-asa-statement-relevant-r-resources/)]
- The 9 Best Marketing And Sales Analytics You Should Know About.[[Data Science Central](http://www.datasciencecentral.com/profiles/blogs/the-9-best-marketing-and-sales-analytics-you-should-know-about)]
- Cohort analysis. [[Youtube](https://www.youtube.com/watch?v=NyhVdGmnh0I)]
- Ted Talk : How to use data to make a hit TV show. [[Ted](http://www.ted.com/talks/sebastian_wernicke_how_to_use_data_to_make_a_hit_tv_show?utm_campaign=social&utm_medium=referral&utm_source=facebook.com&utm_content=talk&utm_term=technology)]

@@

# Learn Data Science

- The MBA Data Science Toolkit: 8 resources to go from the spreadsheet to the command line. [[Medium](https://medium.com/@dmca/the-mba-data-science-toolkit-8-resources-to-go-from-the-spreadsheet-to-the-command-line-cbb59ea82144#.pjph91n3m)]

### 2016-04-18 bayesian_statistics/MCMC/MCMC.Rmd
to do mcmc
organize folder

@@

Some probability distributions, like the Normal distribution and the Poisson distribution, are relatively straightforward to work with mathematically and we have lots of handy tools for working with them by hand and on the computer.

Other probability distributions over parameters in a complicated model are harder to work with. In this case we need more general tools. **Monte Carlo** methods work by taking samples from a distribution that's hard to study analytically, and then studying the samples instead.

@@

Of course, this is a toy example. It turns out that you may end up throwing away exponentially more attempts per successful sample as the number of dimensions in your data goes up. So hardly anyone uses rejection sampling without a good reason -- that's where the Markov chains come in.

@@

That's where the Markov chains come in. MCMC has exactly the same goal as our rejection sampler, but it has more sophisticated ways of deciding where to sample, which can be expressed at a high level as follows:

@@

- Inference using the first few thousand points is a bad idea, as they are unrelated to the final distribution we are interested in, or in other words, the first few moves of the algorithm are not reflective of the posterior. Thus is it a good idea to discard those samples before using the samples for inference. We call this period before converge the **burn-in** period.
- The algorithm can be seen as a random "walk" around the space, thus the current position will exhibit some correlation with previous positions. This is both good and bad. We will always have correlation between current positions and the previous positions, but too much of it means we are not exploring the space well. The correlation can be solved, or at least reduced, by only returning to the user every nth sample. We call this **thinning**.

@@

MCMC <- function( iter, burnin = 0, thin = 1 )
{
	# the list of the first argument for dimnames is to specify the row names,
	# sampling starts at a random point, here 0, 0 
	samples <- matrix( NA, nrow = iter, ncol = 2, 
					  dimnames = list( NULL, c( "x", "y" ) ) )
	samples[ 1, ] <- c( 0, 0 )

@@

			# propose a new sample point			
			proposal <- sample + rnorm( n = 2, mean = 0, sd = 1 )

@@

**End Note:**

@@

**Sources:**

Code to the documentation can be found [here](https://github.com/ethen8181/Business-Analytics/blob/master/bayesian_statistics/MCMC/MCMC.R).

@@

>>>>

> To follow along, code to the documentation can be found [here](https://github.com/ethen8181/Business-Analytics/blob/master/bayesian_statistics/MCMC/MCMC.R).

@@

Some probability distributions, like the Normal distribution and the Poisson distribution, are relatively straightforward to work with mathematically and we have lots of handy tools for working with them by hand and on the computer. Other probability distributions over parameters in a complicated model are harder to work with. In this case we need more general tools.

*Markov Chain Monte Carlo (MCMC)* is a class of methods in which we can simulate draws (taking samples) that are slightly dependent and are approximately from a (posterior) distribution. We then take those draws and calculate quantities of interest for the (posterior) distribution. In Bayesian statistics, there are generally two MCMC algorithms that we use: the **Gibbs Sampler** and the **Metropolis-Hastings algorithm**.

In short, MCMC methods work by taking samples from a distribution that's hard to study analytically, and then study on their samples instead.

@@

Of course, this is a toy example. It turns out that you may end up throwing away exponentially more attempts per successful sample as the number of dimensions in your data goes up. So hardly anyone uses rejection sampling without a good reason.

@@

That's where MCMC methods comes in. MCMC has exactly the same goal as our rejection sampler, but it has more sophisticated ways of deciding where to sample, which can be expressed at a high level as follows:

@@

- Inference using the first few thousand points is a bad idea, as they are unrelated to the final distribution we are interested in, or in other words, the first few moves of the algorithm are not reflective of the posterior. Thus is it a good idea to discard those samples before using the samples for inference. We call this period before converge the **burn-in** period.
- The algorithm can be seen as a random "walk" around the space, thus the current position will exhibit some correlation with previous positions. This is both good and bad. We will always have correlation between current positions and the previous positions, but too much of it means we are not exploring the space well. The correlation can be solved, or at least reduced, by only returning to the user every nth sample. We call this **thinning**. e.g. when **thinning** by 2, only sample points at step 1, 3, 5, 7 and so on, are retained. Note that although the thinned sample points tend to be less correlated than the original ones, they can also contain less information and it takes longer to run (reduces sampling efficiency).

@@

# Metropolis-Hastings algorithm (will elaborate on this later)
MCMC <- function( iter, burnin = 0, thin = 1 )
{
	# the list of the first argument for dimnames is to specify the row names,
	# sampling starts at a random point, here 0, 0 
	samples <- matrix( NA, nrow = iter, ncol = 2, 
					   dimnames = list( NULL, c( "x", "y" ) ) )
	samples[ 1, ] <- c( 0, 0 )

@@

			# propose a new sample point (will elaborate on this later)			
			proposal <- sample + rnorm( n = 2, mean = 0, sd = 1 )

@@

@@

## Gibbs Sampling

The MCMC method we've introduced above is also known as the *Metropolis-Hastings algorithm*. It is very general and broadly applicable, but one drawback is that your proposed distribution has to be properly tuned to the posterior distribution. Recall that we proposed a new random sample point using the a normal distribtuion with the mean of 1 and standard deviation of 1 `rnorm( ..., mean = 0, sd = 1 )`. If this random sample point generator's distribution is too wide or too narrow, a large proportion of our proposed sample point will still be rejected. Or more intuitively, the effectiveness of our random walk will farely low.

Given this situation, there's an alternative sampling algorithm called **Gibbs Samplinig**. Unlike the **Metropolis Sampling**, with **Gibbs Samplinig**  all proposed jumps are accepted.

## Takeaways

- If you can decompose your probability distribution into conditional probabilities, then **Gibbs Samplinig** is preferable over **Metropolis Sampling**.

@@

## R Session Information

sessionInfo()

### 2016-04-18 marketing_analysis/marketing_analysis.Rmd
organize folder

---
title: "Marketing Analysis"
author: "Ming-Yu Liu"
date: "December 20, 2015"
output: 
  html_document: 
    highlight: haddock
    number_sections: yes
    theme: united
    toc: yes
---

## Background Information

@@

## Segmentation

@@

# environment setting
library(grid)
library(dplyr)
library(ggplot2)
library(gridExtra)
library(lubridate)
library(data.table)
setwd("/Users/ethen/Business-Analytics/2_marketing_analysis")

@@

source("/Users/ethen/Business-Analytics/2_marketing_analysis/code/marketing_functions.R")
rfm1 <- Segmentation( data = rfm1, inactive = inactive, 
					  cold = cold, warm = warm, amount = amount )
rfm1

@@

## Customer Life Time Value

@@

**Takeaways:**

1. Use statistical segmentation when the segment you wish to obtain is a "oneshot" thing or use it as a exploratory tool when you're not famaliar with the overall objective.

@@

You can find all the source code [here](https://github.com/ethen8181/Business-Analytics/tree/master/2_marketing_analysis/code). marketing_analysis.R contains the documentation's general scripts and marketing_functions.R contains the functions that were sourced in and used with this documentation.

@@

## R Session Information

>>>>

---
title: "Marketing Analysis"
author: "Ming-Yu Liu"
date: "`r Sys.Date()`"
output:
  rmdformats::readthedown:
    highlight: pygments
---

@@

# Segmentation

@@

# environment setting
library(grid)
library(dplyr)
library(ggplot2)
library(gridExtra)
library(lubridate)
library(data.table)
setwd("/Users/ethen/Business-Analytics/marketing_analysis")

@@

source("/Users/ethen/Business-Analytics/marketing_analysis/code/marketing_functions.R")
rfm1 <- Segmentation( data = rfm1, inactive = inactive, 
					  cold = cold, warm = warm, amount = amount )
rfm1

@@

**Section Takeaways:** Use statistical segmentation when the segment you wish to obtain is a "oneshot" thing or use it as a exploratory tool when you're not famaliar with the overall objective.

# Customer Life Time Value

@@

@@

You can find all the source code [here](https://github.com/ethen8181/Business-Analytics/tree/master/marketing_analysis/code). marketing_analysis.R contains the documentation's general scripts and marketing_functions.R contains the functions that were sourced in and used with this documentation.

@@

# R Session Information
